---
title: "Week02-assignment"
author: "YOUR NAME HERE"
date: "TODAY's DATE HERE"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Libraries used in this document 

For the tasks below, we'll be using **ggplot2** package, which is part of the **tidyverse**

```{r}
library(tidyverse)
```

## Class assignments for Week 02 

### TASK 1: Load the *mpc62_clean.csv* and MPC62.DAT data files  

Load the dataset and create create a data frame as an object. Use the assignment operator <-

```{r import_mpc62}

```

### TASK 2: Confirm that the data shos no evidence of non-normality  

Create the following charts using **ggplot()**:  
- "Run plot" using geom_point  
- Histogram  
- Q-Q plot (include **geom_qq** and **geom_qq_line** as layers)  
- Lag plot using by using the **lag()** function when mapping the aesthetics within **ggplot**.  

```{r run_plot}

```

```{r histogram}

```

```{r qq_plot}

```

```{r lag_plot}

```


### TASK 3: Create named objects using base R functions 

- Calculate the mean value for the 25 average daily measurements.
- Calculate the level-2 standard deviation for the 25 average daily measurements.
- Calculate the level-1 standard deviation (pooled) for the daily standard deviations.

```{r named_objects}

```



### TASK 4: Calcluate test statistics  

Confirm you can reproduce the results from example [2.6.2.5 from the NIST Handbook](https://www.itl.nist.gov/div898/handbook/mpc/section6/mpc625.htm)

- Calculate the t-test statistic using the `qt()` function
- Calculate the F-test statistic using the `qf()` function

```{r test_stats}

```


### TASK 5: Create a Shewhart control chart 

```{r shewhart_chart}

```


### TASK 6: Create a control chart for precision 

```{r level1_chart}

```










